---
title: "BernieTweet"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Libraries needed:
```{r message=FALSE, warning=FALSE}
library(rtweet)
library(stringr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(scales)
library(tidytext)

```
## Get Bernie Sanders timeline

```{r warning=FALSE}
tmls <- get_timelines('BernieSanders', n = 3200)
tweets <- tmls %>% select(status_id, source, text, created_at, favorite_count, retweet_count) 
tweets <- mutate(tweets,source =ifelse(str_detect(tweets$source,'(?<=Twitter )[^.]*')==TRUE,str_match(tweets$source, '(?<=Twitter )[^.]*'), tweets$source))
```

## Show source of tweets from \@BernieSanders

```{r, echo=FALSE}
tweets$source[tweets$source == 'for iPad'] <-'iPad'
tweets$source[tweets$source == 'for iPhone'] <-'iPhone'
tweets$source[tweets$source == 'for Android'] <-'Android'
tweets$source<- gsub(" ","",tweets$source)
tweets_count <-tweets %>% count(source)
tweets_count
```

## Bar plot
Web Client is the most used source to make tweets, Tweet Deck coming in second and iPhone coming in third place.

```{r,echo=FALSE}
tweets_count %>% ggplot(aes(y =n ,x =source, fill = source)) + 
  geom_bar(width = 1, stat = "identity")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Hourly

Usual time of the day where Twitter source is made from:

```{r ,echo=FALSE}
tweets %>%
  count(source, hour=hour(with_tz(created_at, "EST")))%>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(hour, percent, color = source)) +
  geom_line() +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Hour of day (EST)",
       y = "% of tweets",
       color = "")
```

## Favorite Tweets
According to users, these are BernieSanders favorites tweets:

```{r}
#favorites
print('Most favorited Tweet:')
tweets[which.max(tweets$favorite_count), ]$text 
print('Least favorited Tweet:')
tweets[which.min(tweets$favorite_count), ]$text
fav_tweets <- tweets %>% filter(favorite_count > mean(tweets$favorite_count))
count(fav_tweets)


#retweet
print('Most retweeted Tweet:')
tweets[which.max(tweets$retweet_count), ]$text
print('Least retweeted Tweet:')
tweets[which.min(tweets$retweet_count), ]$text
re_tweets <- tweets %>% filter(retweet_count > mean(tweets$retweet_count))
count(re_tweets)

```

## Top 5 hashtags used
```{r, echo=FALSE}
tweets %>% 
  unnest_tokens(word,text, token = 'tweets') %>%
  filter(str_detect(word, '^#')) %>%
  count(word, sort = TRUE) %>% head(5)
```

## Word Sentiment
The top 20 words used in the 3200 tweets made by BernieSanders with each frequency
```{r , echo=FALSE}
reg <- "([^A-Za-z\\d#@']|'(?![A-Za-z\\d#@]))"
tweet_words <- tweets %>%
  filter(!str_detect(text, '^"')) %>%
  mutate(text = str_replace_all(text, "https://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
  unnest_tokens(word, text, token = "regex", pattern = reg) %>%
  filter(!word %in% stop_words$word,
         str_detect(word, "[a-z]"))
common_words <- tweet_words %>% count(word, sort=TRUE) %>% head(.,20)
common_words %>% ggplot(aes(y =n ,x =reorder(word,+n))) +  
  ylab("Occurrences") + xlab('Word') +
  geom_bar(width = 0.7, stat = "identity") + coord_flip()
```

What about the top favorite tweets?
```{r , echo=FALSE}


fav_words <- fav_tweets %>%
  filter(!str_detect(text, '^"')) %>%
  mutate(text = str_replace_all(text, "https://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
  unnest_tokens(word, text, token = "regex", pattern = reg) %>%
  filter(!word %in% stop_words$word,
         str_detect(word, "[a-z]"))
common_words <- fav_words %>% count(word, sort=TRUE) %>% head(.,20)
common_words %>% ggplot(aes(y =n ,x =reorder(word,+n))) +  
  ylab("Occurrences") + xlab('Word') +
  geom_bar(width = 0.7, stat = "identity") + coord_flip()

```

## Term Frequency–Inverse Document Frequency,
```{r, echo=FALSE}
tweet_words_count <- tweet_words %>%
  count(source, word, sort = TRUE) %>%
  ungroup()


total_words <- tweet_words_count %>%
  group_by(source) %>%
  summarize(total = sum(n))
total_words

tweet_words_count <- left_join(tweet_words_count, total_words)
tweet_words_count <- tweet_words_count %>%
  bind_tf_idf(word, source, n)

tweet_words_count %>%
  select(-total) %>%
  arrange(desc(tf_idf))

tweet_important <- tweet_words_count %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word))))

tweet_important %>%
  head(30)%>%
  group_by(source) %>%
  slice(1:15) %>%
  ggplot(aes(word, tf_idf, fill = source)) +
  geom_bar(alpha = 0.8, stat = "identity") +
  labs(title = "Highest tf-idf words in @BernieSanders",
       subtitle = "Top 30 ",
       x = NULL, y = "tf-idf") +
  coord_flip()
```

## Sentiment analysis
8 emotions (anger, fear, anticipation, trust, surprise, sadness, joy, and disgust) 
2 sentiments (negative and positive)
**emolex downloaded from http://saifmohammad.com/Lexicons/**
We are looking at the percentage of tweets where each sentiment is shown during the  hour of the day.
A positive sentiment is the highest percentage of tweets

```{r, echo=FALSE}
wd <- getwd()
emolex <- read_table2(
  file.path(wd,"NRC-emotion-lexicon-wordlevel-alphabetized-v0.92.txt"),
  col_names = FALSE,
  skip = 45)
colnames(emolex) <- c("word", "emotion", "value")
# remove values with 0
emolex <- emolex %>%  filter(value > 0)

nrc <-emolex %>%
  select(word, emotion)


#hourly 
tweet_words %>% 
  inner_join(nrc, by = "word")%>%
  count(emotion, hour=hour(with_tz(created_at, "EST"))) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(hour, percent, color = emotion)) +
  geom_line() + geom_path(size = 1) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Hour of day (EST)",
       y = "% of tweets",
       color = "")


#weekly
tweet_words %>% 
  inner_join(nrc, by = "word")%>%
  count(emotion, week=week(with_tz(created_at, "EST"))) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(week, percent, color = emotion)) +
  geom_line() + geom_path(size = 1) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Week (EST)",
       y = "% of tweets",
       color = "")

#monthly
tweet_words%>% 
  inner_join(nrc, by = "word")  %>%
  count(emotion, month=date(created_at))%>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(month, percent, color = emotion)) +
  geom_line() +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Monthly (EST)",
       y = "% of tweets",
       color = "") 


```

## We can look at the past month for a better view
```{r, echo=FALSE}

tweet_words%>% 
  inner_join(nrc, by = "word")  %>%
  count(emotion, month=date(created_at)) %>%
  filter(month > as.Date('2019-08-01')) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(month, percent, color = emotion)) +
  geom_line() +  geom_path(size = 1) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Monthly (EST)",
       y = "% of tweets",
       color = "") 
```

## Favorites?
```{r, echo=FALSE}
fav_words %>% 
  inner_join(nrc, by = "word")%>%
  count(emotion, hour=hour(with_tz(created_at, "EST"))) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(hour, percent, color = emotion)) +
  geom_line() + geom_path(size = 1) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Hour of day (EST)",
       y = "% of tweets",
       color = "")

#weekly
fav_words %>% 
  inner_join(nrc, by = "word")%>%
  count(emotion, week=week(with_tz(created_at, "EST"))) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(week, percent, color = emotion)) +
  geom_line() + geom_path(size = 1) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Week (EST)",
       y = "% of tweets",
       color = "")

#monthly
fav_words%>% 
  inner_join(nrc, by = "word")  %>%
  count(emotion, month=date(created_at))%>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(month, percent, color = emotion)) +
  geom_line() +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Monthly (EST)",
       y = "% of tweets",
       color = "") 

fav_words%>% 
  inner_join(nrc, by = "word")  %>%
  count(emotion, month=date(created_at)) %>%
  filter(month > as.Date('2019-08-01')) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(month, percent, color = emotion)) +
  geom_line() +  geom_path(size = 1) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Monthly (EST)",
       y = "% of tweets",
       color = "") 


```


## Sentiments per source
``` {r, echo=FALSE}
sources <- tweet_words %>%
  group_by(source) %>%
  mutate(total_words = n()) %>%
  ungroup() %>%
  distinct(status_id, source, total_words)

sources[order(sources$total_words, decreasing = TRUE),]

by_source_sentiment <- tweet_words %>%
  inner_join(nrc, by = "word") %>%
  count(emotion, status_id) %>%
  ungroup() %>%
  complete(emotion, status_id, fill = list(n = 0)) %>%
  inner_join(sources, "status_id") %>%
  group_by(source, emotion, total_words) %>%
  summarize(words = sum(n)) %>%
  ungroup()

head(by_source_sentiment)

by_source_sentiment %>%
  ggplot(aes(source, words,fill=emotion)) + 
  geom_bar(width = 0.7, stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

by_source_sentiment %>%
  ggplot(aes(emotion, words,fill=source)) + 
  geom_bar(width = 0.7, stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

Compared to favorites, no huge difference except tweets from Periscope source are less liked.

```{r, echo=FALSE}
sources_fav <- fav_words %>%
  group_by(source) %>%
  mutate(total_words = n()) %>%
  ungroup() %>%
  distinct(status_id, source, total_words)

sources_fav[order(sources$total_words, decreasing = TRUE),]

by_source_sentiment_fav <- fav_words %>%
  inner_join(nrc, by = "word") %>%
  count(emotion, status_id) %>%
  ungroup() %>%
  complete(emotion, status_id, fill = list(n = 0)) %>%
  inner_join(sources, "status_id") %>%
  group_by(source, emotion, total_words) %>%
  summarize(words = sum(n)) %>%
  ungroup()

head(by_source_sentiment_fav)

by_source_sentiment_fav %>%
  ggplot(aes(source, words,fill=emotion)) + 
  geom_bar(width = 0.7, stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

by_source_sentiment_fav %>%
  ggplot(aes(emotion, words,fill=source)) + 
  geom_bar(width = 0.7, stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



